Lab News

### 2024-01-21 index.qmd
update news with new paper

@@

<font color="#d08770">[September 6 2023].</font> **Paper accepted**.   Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*.

@@

<font color="#d08770">[June 20 2023].</font> **New award**. Congratulations to Laura St. Germain (Ph.D. Candidate) on winning the 2023 Franklin Henry Young Scientist Award in Motor Control and Learning from the Canadian Society for Psychomotor Learning and Sport Psychology.

>>>>

<font color="#d08770">[January 22 2024].</font> **Paper accepted**. Roth, A.M., Lokesh, R., Tang, J., Buggeln, J.H., Smith, C., Calalo, J.A., Sullivan, S.R., Ngo, T., St. Germain, L., Carter, M.J., & Cashaback, J.G.A. Punishment leads to greater sensorimotor learning but less movement variability compared to reward. *Neuroscience*. <https://doi.org/10.1016/j.neuroscience.2024.01.004>

@@

<font color="#d08770">[September 6 2023].</font> **Paper accepted**. Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*. <https://doi.org/10.1098/rspb.2023.1475>

@@
